Ice sheet mass flows

### 2024-06-24 ms.tex
Brice is co-author
There is an implicit physical flow

\author[Mankoff and others]
       {Kenneth D. MANKOFF,$^{1,2}$
         Xavier FETTWEIS,
         Chad GREENE,
         Someone, ELSE,$^n$,
       add your name to CREDIT.CSV in repository}

@@

  The flows can be somewhat tied to physical space as in the Minard map mentioned above, but are not done so explicitly here. An similar display to the diagrams presented here, of glacier mass flow by \citet[Fig. 2]{cogley_2011}, shows flow overlaid an a glacier schematic, but with neither flow magnitude nor proportionality.

>>>>

\author[Mankoff and others]
       {Kenneth D. MANKOFF,$^{1,2}$
         Xavier FETTWEIS,
         Chad GREENE,
         Brice VAN LIEFFERINGE,
         Someone, ELSE,$^n$,
       add your name to CREDIT.CSV in repository}

@@

  The flows can be somewhat tied to physical space as in the Minard map mentioned above, but are not done so explicitly here. An similar display to the diagrams presented here, of glacier mass flow by \citet[Fig. 2]{cogley_2011}, shows flow overlaid an a glacier schematic, but with neither flow magnitude nor proportionality. Nonetheless, there is an implicit physical connection here for most flow. Inputs all come from the atmosphere (with the exception of drawdown and frontal advance), and outputs pointing down are all mass flow into the ocean.
